Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-02-03 paper/zhang-cook-laa-langrene-menendez.Rmd
underscore to dash in tour-path.png

```{r tour-path, out.height="20%",out.width="50%", fig.cap="Each square (frame) represents the projected data with a corresponding basis. Blue frames are found by an optimisation algorithm iteratively whilst the white frames are constructed between two blue frames by geodesic interpolation."}
include_graphics(here::here("img/tour_path.png"))
```

>>>>

```{r tour-path, out.height="20%",out.width="50%", fig.cap="Each square (frame) represents the projected data with a corresponding basis. Blue frames are found by an optimisation algorithm iteratively whilst the white frames are constructed between two blue frames by geodesic interpolation."}
include_graphics(here::here("img/tour-path.png"))
```
